---
title: "Information, Power, and Agendas: Drivers of (In)Attention to Climate Change"
bibliography: references.bib
csl: american-political-science-association.csl
fig-cap-location: top
fontfamily: ebgaramond
link-bibliography: false
format:
  html:
    author:
      - name: Matthew C. Nowlin
        email: matthew.nowlin@uta.edu
        corresponding: true
        affiliations:
          - name: University of Texas at Arlington
            department: Department of Political Science
      - name: Jonathan Lewallen
        email: jlewallen@ut.edu
        affiliations:
          - name: University of Tampa
            department: Political Science and International Studies
  pdf:
    author:
      - name: "Matthew C. Nowlin^[Associate Professor, Department of Political Science, University of Texas at Arlington. Email: matthew.nowlin@uta.edu]"
      - name: "Jonathan Lewallen^[Associate Professor, Department of Political Science and Internaitonal Relations, University of Tampa. Email: jlewallen@ut.edu]"
    include-in-header:
      text: |
        \usepackage{setspace}
        \usepackage{dcolumn}
        \usepackage{float}
        \usepackage{amsmath}
        \addtokomafont{disposition}{\rmfamily}
        \normalem
  docx:
    author:
      - name: "Matthew C. Nowlin^[Associate Professor, Department of Political Science, University of Texas at Arlington. Email: matthew.nowlin@uta.edu]"
      - name: "Jonathan Lewallen^[University of Tampa. Email: jlewallen@ut.edu]"
    reference-doc: custom-reference-doc.docx
---

```{r}
#| include: false
source("scripts/analysis.R")
```

# Introduction 


# Agenda Setting and Agenda Denial 

# Information Environment 

# Data and Measures

We first replicate and extend the analysis of @liuExplainingMediaCongressional2011

The dependent variable is the annual count of congressional hearings addressing climate change, first assembled by @liuExplainingMediaCongressional2011 from LexisNexis Congressional Publications for 1969 to 2005, and extended by @nowlinEnvironmentalPolicymakingEra2019 through 2016 using ProQuest Congressional. Institutional access to ProQuest was no longer available for this extension, so I identified hearings from 2017 through 2022 through a committee-scoped enumeration of the GovInfo Congressional Hearings collection, screened by hearing title and then by the opening statement of the hearing transcript, and calibrated the resulting counts against the known 2013 to 2016 totals. I cross-checked the resulting annual pattern against a second, independent instrument built from congress.gov's committee-meeting records. Trial ProQuest access obtained later in the project allowed me to add 2023 and 2024 using a title-based screen and to extend the series back to 1969, the first year of the original series. The earliest hearing in ProQuest matching the same search terms used throughout occurs in 1976, and a hand search of ProQuest Congressional returned no climate change hearings between 1969 and 1975, so I coded those years as zero. The final series spans 1969 to 2024.

The independent variables replicate the problem indicators, focusing events, scientific feedback, and partisan control measures used by @liuExplainingMediaCongressional2011, extended through 2024 and back to 1969. I pulled the net Keeling level and the Climate Extremes Index directly from NOAA's public data services, and both matched closely to the original 1980 to 2016 values, so I spliced these two series onto the original data rather than replacing them. Media attention, measured as the annual count of *New York Times* articles matching the same search terms as the hearings measure, could not be spliced in the same way. Searching today's version of the *New York Times* Article Search API returned counts several times larger than the original totals for the overlapping years, with a gap that grew over time, likely reflecting how much broader the index has become since the original data were collected, so I refreshed this series entirely on current data rather than mix two incompatible scales. Scientific feedback is measured as the net annual change in climate-related publications indexed in Web of Science. Searching today's Web of Science returned about 60 percent of the original annual counts, a ratio that held steady from the mid-1990s through 2016, so I kept the original values for 1980 to 2016 and added the annual changes from the current search for later years, rescaled by that ratio. For 1969 to 1979, when Web of Science indexes few abstracts and the counts are near zero, I used the current changes without rescaling. I identified international focusing events by applying @liuExplainingMediaCongressional2011's own four-part definition, an unprecedented international agreement, a new international institution, a high-profile international convention, or a landmark scientific assessment, to candidate events from 2006 through 2024, and coded them as a single dummy variable following the original study. I coded Republican control of Congress from the historical party composition of the House and Senate in each year.

```{r}
#| label: fig-hearings
#| fig-cap: "Congressional Climate-Change Hearings, 1969-2024"
fig_hearings
```

```{r}
#| label: fig-indicators
#| fig-cap: "Problem Indicators, 1969-2024"
fig_indicators
```

# Results

```{r}
#| label: tbl-liu-var
#| tbl-cap: "Media and Congressional Attention to Climate Change, 1969-2024"
tbl_liu_var
```

```{r}
#| label: tbl-liu-var-2005
#| tbl-cap: "Media and Congressional Attention to Climate Change, 1969-2005 (cf. Liu et al. 2011)"
tbl_liu_var_2005
```

\newpage

# References